Paper 1 Analysis

### 2015-12-07 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Trying new version of models graph.

  # Now make the plot
  ggplot() +
  geom_line(alpha = 0.8, aes(x = Year, 
                             y = y_value,
                             group = y_type,
                             color = y_type,
                             linetype = y_type,
                             size = y_type)
  ) + 
  facet_grid(yfacet ~ xfacet) + 
  scale_x_continuous(limits = c(1955, 2013), breaks = c(1960, 1980, 2000)) +
  scale_y_continuous(limits = c(0.5, 7), breaks = c(1, 2, 4, 6)) +
  scale_color_manual(
    name = "",
    labels = c("historical", "fitted"),
    values=c("gray70", "black")
  ) +
  scale_size_manual(
    name = "",
    labels = c("historical", "fitted"),
    values = c(1.5, 0.3)) +
  scale_linetype_manual( 
    name = "",
    labels = c("historical", "fitted"),
    values=c(1,1) ) + 
  labs(x="", y="Indexed GDP (1960 = 1)") +
  xy_theme()

>>>>

  # Now make the plot
  ggplot() +
  geom_line(alpha = 0.8, aes(x = Year, 
                             y = y_value,
                             group = y_type,
                             color = y_type,
                             linetype = y_type,
                             size = y_type)
  ) + 
  facet_grid(yfacet ~ xfacet) + 
  scale_x_continuous(limits = c(1955, 2013), breaks = c(1960, 1980, 2000)) +
  scale_y_continuous(limits = c(0.5, 7), breaks = c(1, 2, 4, 6)) +

  # We had this code for a while
#   scale_color_manual(
#     name = "",
#     labels = c("historical", "fitted"),
#     values=c("gray70", "black")
#   ) +
#   scale_size_manual(
#     name = "",
#     labels = c("historical", "fitted"),
#     values = c(1.5, 0.3)) +
#   scale_linetype_manual( 
#     name = "",
#     labels = c("historical", "fitted"),
#     values=c(1,1) ) + 
#   labs(x="", y="Indexed GDP (1960 = 1)") +

  # But Paul suggests some small changes:

  scale_color_manual(
    name = "",
    labels = c("historical", "fitted"),
    values=c("black", "black")
  ) +
  scale_size_manual(
    name = "",
    labels = c("historical", "fitted"),
    values = c(0.2, 0.2)) +
  scale_linetype_manual( 
    name = "",
    labels = c("historical", "fitted"),
    values=c(1,2) ) + 
  labs(x="", y="Indexed GDP (1960 = 1)") +

  xy_theme()
